Discussion Draft

### 2020-04-09 doc/Discussion.rmd

---
title: "Discussion Draft"
date: ''
output:
  word_document:
    toc: yes
    toc_depth: '5'
  pdf_document: default
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
bibliography: refs_Main_Report.bib
---

@@

<leaky oocyte SAC linked to acentrosome spindle (multiple aMTOCs) and cell volume, these are features which differ in spermatocyttes (small, centrosome spindle, 2MTOCs)>

<Directional selection could be the result in spermatogenesis if the fitness landscape for 'chromosome structure' is altered via genetic architecture changes or GxE effects. (in oogenesis the leaky SAC has weak selection coefficient)>

@@

@@

@@

# consequences of longer female axis - 
# (normalzed interference strength due to axis differences / Chromtain loop length)
#

@@

@@

<Still working on Future Steps>

>>>>

---
title: "Discussion Draft"
date: ''
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_Main_Report.bib
---

@@

**if none of the models turn out to be appropriate,** it 
could be due to assumptions we made regaurding....

**We also note that** The musculus and molossinus subspecies have more shared ancestry (compared to domesticus) (cite Geraldes?), so we  cant determine if the rapid male evolution in gwrr are independant (mulitple events) or due to incomplete lineage sorting (single event).

If these hypotheses turn out to not be true, (a prediction that can be made, due to the rapid male specific

The consequences of this reversed heterochismy in house mice is that the sex-average / species average of gwRR is higher. meaning/resulting lower ld overall.

@@

If these hypotheses turn out to not be true, (a prediction that can be made, due to

The consequences of this difference in meitic events -- (it fits follows from some basic differences in reproductive stategies between males and females) -- females diversify offspring, males --

-- predictions for adaptations to changing environments -- but applied to short timescales -- since all the genes go back in the other sex the fllowing generation.

@@

If these hypotheses concerning evolution of these patterns are not true -- there's still predictions that can be made given the consequences of these patterns. The consequences of this difference in the typical landscape as reviewed in [@sardell_sex_2020]. For the sex averaged landscape along chromosomes, any diviation from uniform placement is generally due to male specific patterns.

-- There's also the prediction that females have active CO supression near telomeres 
(variation) -- geiven the evidence in (female mice) that show a higher elevation of DSBs at the telomere (halldorsson?).

@@

# consequences of longer female axis - 
# (normalzed interference strength due to axis differences / Chromtain loop length)

@@

 consequences of longer female axis - 
 (normalzed interference strength due to axis differences / Chromtain loop length)

We also hypothesize that the sex differences in chromatin structure are closely connected to sex differences  in the interference strength and our results mirror those in [@petkov2007] and follow the prediction that shorter-loop will have stronger interference.

According to the tethered loop model of DSB formation (cite schmenti?), the 'real estate' for COs are the chromatin / DNA loops, the density of whch is conserved in the axis and loop formation (later the SC str), so the number of loops is equvilent to the length of the axis. **The chromosomes are converted to a 2D space (the axis length of a given chromosome is the limited factor for total CO number)**.  Only one of the models COM aligns with our observed results for sexual dimorphism for axis length. **COM** predicts that axis length will be larger in oocytes due to the larger volume.

@@

None of these models may be appropriate due to X Y and  Z caveats. The consequence of this pattern of greater interference strength is ---
 consequence of rapid evolution of normalized interference strength, larger linkage blocks.

#Future steps

<importance of evolutionary distinct trajectories, measure both sexes -- do evolutionary comparisons within sex.

wild samples, short times scales.

single cell measures

chromatid interference

integrate physical models -- centromere and kinetochore

>
